Downloading the 2012 IPEDS data
===============================

2012 IPEDS (final release) data were downloaded from the IPEDS data center website

[http://nces.ed.gov/ipeds/datacenter/CDSPreview.aspx](http://nces.ed.gov/ipeds/datacenter/CDSPreview.aspx)

on June 3, 2014 using the 380 institutions in Minnesota, Wisconsin, Illinois, Indiana, Michigan, and Ohio found in the file

`C:\research\IPEDS\data\DC_InstGroup_62232_upper_midwest.uid`

Here are the download instructions:

1. [http://nces.ed.gov/ipeds/datacenter/Default.aspx](http://nces.ed.gov/ipeds/datacenter/Default.aspx)
2. Click "Download custom data files"
3. Select "Use final release data" (default) and click "Continue"
4. Select institutions by clicking the "Uploading a file" link.
5. Login in.
6. Upload the `DC_InstGroup_62232_upper_midwest.uid` file and click "Submit".
7. In the "Select Variables" tab, click on one of the ten categories of variables.  
8. Click to open all of the subcategories and "select all variables" within each subcategory.
9. When finished with a category, click the "Continue" button near the top of the page.
10. On the results tab, do not impute data, and click the CSV link to get a zip file with CSV data and an HTML codebook.
11. Click "Start Over" and repeat this process on another of the ten categories.

I saved the files in `data/2012/raw/nn_descriptive_name.csv` and similarly for the html codebook files.

Instructions for how to use the IPEDS datacenter can be found at [https://nces.ed.gov/ipeds/datacenter/IPEDSManual.pdf](https://nces.ed.gov/ipeds/datacenter/IPEDSManual.pdf)

----

Processing the 2012 IPEDS Raw Data into Analytic Data
=====================================================

Eventually, this script will load the raw 2012 IPEDS data and process it into a tidy data set suitable for analysis.  Right now, it just loads the data files I downloaded and prints out some information.


Category 1: Frequently used derived variables
---------------------------------------------

```{r}
df1 <- read.csv("2012/raw/01_Frequently_used_derived_variables.csv")
dim(df1)
names(df1)
str(df1)
```



Category 2: Institutional characteristics
---------------------------------------------

```{r}
df2 <- read.csv("2012/raw/02_Institutional_characteristics.csv")
dim(df2)
names(df2)
str(df2)
```


Category 3: Enrollments
---------------------------------------------

```{r}
df3_1 <- read.csv("2012/raw/03_Enrollments_1.csv")
dim(df3_1)
names(df3_1)
#str(df3_1)

df3_2 <- read.csv("2012/raw/03_Enrollments_2.csv")
dim(df3_2)
names(df3_2)
#str(df3_2)

df3_3 <- read.csv("2012/raw/03_Enrollments_3.csv")
dim(df3_3)
names(df3_3)
#str(df3_3)

df3_4 <- read.csv("2012/raw/03_Enrollments_4.csv")
dim(df3_4)
names(df3_4)
#str(df3_4)

df3_5 <- read.csv("2012/raw/03_Enrollments_5.csv")
dim(df3_5)
names(df3_5)
#str(df3_5)

df3_6 <- read.csv("2012/raw/03_Enrollments_6.csv")
dim(df3_6)
names(df3_6)
#str(df3_6)

df3_7 <- read.csv("2012/raw/03_Enrollments_7.csv")
dim(df3_7)
names(df3_7)
#str(df3_7)

df3_8 <- read.csv("2012/raw/03_Enrollments_8.csv")
dim(df3_8)
names(df3_8)
#str(df3_8)

```

Category 4: Completions
-----------------------

```{r}
df4_1 <- read.csv("2012/raw/04_Completions_1.csv")
dim(df4_1)
names(df4_1)
#str(df4_1)

df4_2 <- read.csv("2012/raw/04_Completions_2.csv")
dim(df4_2)
names(df4_2)
#str(df4_2)

df4_3 <- read.csv("2012/raw/04_Completions_3.csv")
dim(df4_3)
names(df4_3)
#str(df4_3)

df4_4 <- read.csv("2012/raw/04_Completions_4.csv")
dim(df4_4)
names(df4_4)
#str(df4_4)

```

Category 5: Graduation rates
----------------------------

```{r}
df5_1 <- read.csv("2012/raw/05_Graduation_rates_1.csv")
dim(df5_1)
names(df5_1)
#str(df5_1)

df5_2 <- read.csv("2012/raw/05_Graduation_rates_2.csv")
dim(df5_2)
names(df5_2)
#str(df5_2)
```


Category 6: Student financial aid and net price
-----------------------------------------------

```{r}
df6 <- read.csv("2012/raw/06_Student_financial_aid_and_net_price.csv")
dim(df6)
names(df6)
#str(df6)
```


Category 7: Student financial aid and net price
-----------------------------------------------

```{r}
df7 <- read.csv("2012/raw/07_Finance.csv")
dim(df7)
names(df7)
#str(df7)
```


Category 8: Instructional staff / salaries
------------------------------------------

```{r}
df8_1 <- read.csv("2012/raw/08_Instructional_staff_salaries_1.csv")
dim(df8_1)
names(df8_1)
#str(df8_1)

df8_2 <- read.csv("2012/raw/08_Instructional_staff_salaries_2.csv")
dim(df8_2)
names(df8_2)
#str(df8_2)
```


Category 9: Fall staff
------------------------------------------

```{r}
df9_1 <- read.csv("2012/raw/09_Fall_staff_1.csv")
dim(df9_1)
names(df9_1)
#str(df9_1)

df9_2 <- read.csv("2012/raw/09_Fall_staff_2.csv")
dim(df9_2)
names(df9_2)
#str(df9_2)

df9_3 <- read.csv("2012/raw/09_Fall_staff_3.csv")
dim(df9_3)
names(df9_3)
#str(df9_3)

df9_4 <- read.csv("2012/raw/09_Fall_staff_4.csv")
dim(df9_4)
names(df9_4)
#str(df9_4)

df9_5 <- read.csv("2012/raw/09_Fall_staff_5.csv")
dim(df9_5)
names(df9_5)
#str(df9_5)

```


Category 10: Employees by assigned position
-------------------------------------------

```{r}
df10_1 <- read.csv("2012/raw/10_Employees_by_assigned_position_1.csv")
dim(df10_1)
names(df10_1)
str(df10_1)

df10_2 <- read.csv("2012/raw/10_Employees_by_assigned_position_2.csv")
dim(df10_2)
names(df10_2)
str(df10_2)
```


